Diffusion in Cool Domains with BIEs

### 2021-07-01 docs/diffusion/diffusion.tex
fixed section structuring
layed out first pass at numerical examples

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computing the Flux}
\label{sec:flux}
\begin{itemize}
  \item Need normal derivative of double-layer potential
  \item Trick where we add and subtract normal derivative of Laplace DLP
  \item Expected rate of convergence (we still don't fully understand
    this).
\end{itemize}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Flux}
\label{sec:flux}
\begin{itemize}
  \item Need normal derivative of double-layer potential
  \item Trick where we add and subtract normal derivative of Laplace DLP
  \item Expected rate of convergence (we still don't fully understand
    this).
\end{itemize}

@@

\subsection{Example 1}
\begin{itemize}
  \item Analytic solution such as circle in an infinite domain 
  \item Boundary condition is 0 on the boundary of the circle
  \item Initial condition is $C_0$ everywhere off the boundary of the
    circle
  \item Use Laplace-DLP-Talbot to compute u(x,t) at several time steps
  \item Provide a convergence study using the exact solution
  \item Provide a convergence study of the flux through the body
\end{itemize}

\subsection{Example 2}
\begin{itemize}
  \item More general shape, but only 1 of them (star, crescent, ellipse)
\end{itemize}

\subsection{Example 3}
\begin{itemize}
  \item Multiply-connected with all bodies having a Dirichlet boundary
    condition
\end{itemize}

\subsection{Example 4}
\begin{itemize}
  \item Multiply connected with some domains insulated (Neumann) and
    others kept at a fixed temperature (Dirichlet)
\end{itemize}

\subsection{Example 5}
\begin{itemize}
  \item Multiply connected with insulated bodies and an array of sinks
    at one end and sources at the other
  \item This is just to prove that we can handle different initial
    conditions of the heat equation than just constant ones.
\end{itemize}
